#reading in and manipulating hwinfo graphs for games
```{r}
library(tidyverse)
library(readxl)
library(lubridate) #for date extraction and manipulation
library(ggthemes)
library(tools) #for toTitleCase function (makes strings into propercase)

excel_file_hwinfo = "C:/Users/Ryan/Coding Projects/Computer Benchmark/Data/hwinfo_test.xlsx"

hwinfo_ow <- read_excel(excel_file_hwinfo, sheet = "hwinfo_ow")
hwinfo_destiny <- read_excel(excel_file_hwinfo, sheet = "hwinfo_destiny")
hwinfo_r6 <- read_excel(excel_file_hwinfo, sheet = "hwinfo_r6")
hwinfo_gtav <- read_excel(excel_file_hwinfo, sheet = "hwinfo_gtav")
hwinfo_apex <- read_excel(excel_file_hwinfo, sheet = "hwinfo_apex")
hwinfo_rl <- read_excel(excel_file_hwinfo, sheet = "hwinfo_rl")
hwinfo_battlefront <- read_excel(excel_file_hwinfo, sheet = "hwinfo_battlefront")
hwinfo_halo <- read_excel(excel_file_hwinfo, sheet = "hwinfo_halo")
hwinfo_fortnite <- read_excel(excel_file_hwinfo, sheet = "hwinfo_fortnite")
hwinfo_cod <- read_excel(excel_file_hwinfo, sheet = "hwinfo_cod")


#Creating a list of dataframes from above  
df_list_hw <- list(hwinfo_ow, hwinfo_destiny, hwinfo_r6, hwinfo_gtav, hwinfo_apex, hwinfo_rl, hwinfo_battlefront, hwinfo_halo, hwinfo_fortnite, hwinfo_cod)

# Rename each data frame in the list to match its sheet name
names(df_list_hw) <- c("overwatch", "destiny", "r6", "gtav", "apex", "rocket_league", "battlefront", "halo", "fortnite", "cod")

# Remove the last 2 rows from each data frame
df_list_hw <- lapply(df_list_hw, function(df) head(df, -2))

# Convert all columns (except for the date column) to numeric then recombines original date variable to numeric dataset
df_list_hw <- lapply(df_list_hw, function(df) {
  df_num <- as.data.frame(lapply(df[-1], as.numeric))
  cbind(df[1], df_num)
})

# Rename the date column to "DateTime"
df_list_hw <- lapply(df_list_hw, function(df) {
  names(df)[1] <- "DateTime"
  df
})

# Convert the "DateTime" column to POSIXct format
df_list_hw <- lapply(df_list_hw, function(df) {
  df$DateTime <- ymd_hms(df$DateTime)
  df
})

# Add a "seconds" column representing seconds since the first observation
df_list_hw <- lapply(df_list_hw, function(df) {
  df$seconds <- as.numeric(df$DateTime - min(df$DateTime))
  df
})
```


#Reading in and manipulating frameview graphs 
```{r}
excel_file_frameview = "C:/Users/Ryan/Coding Projects/Computer Benchmark/Data/frameview_files.xlsx"

Frameview_GTAV <- read_excel(excel_file_frameview, sheet = "GTA5")
Frametime_ow <- read_excel(excel_file_frameview, sheet = "Overwatch")
Frametime_R6 <- read_excel(excel_file_frameview, sheet = "RainbowSix")
Frameview_Apex <- read_excel(excel_file_frameview, sheet = "r5apex")
Frameview_Destiny <- read_excel(excel_file_frameview, sheet = "destiny2")
Frameview_RL <- read_excel(excel_file_frameview, sheet = "RocketLeague")

Frameview_battlefront <- read_excel(excel_file_frameview, sheet = "starwarsbattlefrontii")
frameview_halo <- read_excel(excel_file_frameview, sheet = "HaloInfinite")
frameview_fortnite <- read_excel(excel_file_frameview, sheet = "FortniteClient")
frameview_cod <- read_excel(excel_file_frameview, sheet = "cod")

#list of dataframes 

df_list <- list(Frameview_GTAV, Frametime_ow, Frametime_R6, Frameview_Apex, Frameview_Destiny, Frameview_RL, Frameview_battlefront, frameview_halo, frameview_fortnite, frameview_cod)

names(df_list) <- c("gtav", "overwatch", "r6", "apex", "destiny", "rocket_league", "battlefront", "halo", "fortnite", "cod")

# Define the columns to select
cols_to_select <- c("TimeInSeconds", "MsBetweenPresents", "MsBetweenDisplayChange", "GPU1Clk(MHz)", "GPU1Util(%)", "GPU1Temp(C)", "AMDPwr(W) (API)", "CPUClk(MHz)", "CPUUtil(%)", "CPU Package Temp(C)", "CPU Package Power(W)")

# Apply the select statement to each data frame in the list
dfs_all <- lapply(df_list, function(df) select(df, cols_to_select))

# Add the seconds variable to each data frame in the list
dfs_all <- lapply(dfs_all, function(df) {
  df$seconds <- as.numeric(df$TimeInSeconds - min(df$TimeInSeconds))
  return(df)
})

#Way to thin out the observations in my dataset, although it makes no difference at large time intervals, once we zoom in on a specific time thinning out the data helps to smooth the time series graph and avoids it being so jagged  
#This specific code reports values of variables 3 times a second 
dfs_subset <- lapply(dfs_all, function(df) df[seq(1, nrow(df), by = 100), ])

rm(df_list)
```


#Setting what individual game should be displayed for each graph
```{r}
#("gtav", "overwatch", "r6", "apex", "destiny", "rocket_league", "battlefront", "halo", "fortnite", "cod")

game <- "overwatch"
```


#Frametime Graph - need to be careful plotting frametimes because more polls per second may check more issues
```{r}

frametime_plots <- list()

for (df_name in names(dfs_all)) {
  
  frametime <- ggplot(dfs_all[[df_name]], aes(seconds, MsBetweenPresents)) + 
    
  geom_line(color = "blue") +
  labs(
    y = "Frametime",
    x = "Seconds",
    title = paste0("Frametimes for ", df_name)
  ) +
  
  #scale_y_continuous(breaks = seq(0, 20, by = 2), 
                     #limits = c(0, 20)) +
  
  scale_x_continuous(labels = function(x) sprintf("%02d:%02d", floor(x/60), x %% 60)) +
                    
  theme_bw()

  frametime_plots[[df_name]] <- frametime
}

frametime_plots[[game]]


rm(frametime)
```


#GPU and CPU temperature 
```{r}
temperautre_plots <- list()

for (df_name in names(dfs_subset)) {

temp <- ggplot(dfs_subset[[df_name]], aes(seconds)) +
  
    geom_line(aes(y = `CPU Package Temp(C)`, color = "CPU")) +
    
    geom_line(aes(y = `GPU1Temp(C)`, color = "GPU")) +
    
    #Adding the average measure into the graph 
    annotate("text", x = -Inf, y = Inf,
         label = paste0("Avg CPU Temp: ", round(mean(dfs_subset[[df_name]]$`CPU Package Temp(C)`), 2), "\n",
                        "Avg GPU Temp: ", round(mean(dfs_subset[[df_name]]$`GPU1Temp(C)`), 2)),
         size = 2.5, color = "black", hjust = -0.05, vjust = 1.1) +
    
    labs(
      y = "Temperature (*C)",
      x = "Time - Minute:Seconds", 
      title = paste0("Comparing different measures of CPU Temp over time in ", toTitleCase(df_name))
    ) +
    
    scale_x_continuous(
      breaks = seq(0, max(dfs_subset[[df_name]]$seconds), by = 10),
      
      #sprintf() is a function in R that allows you to format strings with placeholders for variables. It takes two arguments: the format string and the variables to substitute into the string. The format string is a character string that includes placeholders for the variables.
      
      labels = function(x) sprintf("%02d:%02d", floor(x/60), x %% 60)
    ) +
    
    scale_y_continuous(breaks = seq(50, 75, by = 5),
      #minor_breaks = seq(40, 80, by = 2.5),
      limits = c(50, 75)) +
    
    scale_color_manual(name = NULL,
                       values = c("CPU" = "red", "GPU" = "blue")) +
  
  theme_clean() +
    
    theme(panel.grid.minor.y = element_line(color = "gray", linetype = "dotted"),
         legend.direction = "horizontal",
         legend.position = c(0.85, 0.88),
         legend.text = element_text(size = 6),
         legend.background = element_rect(fill = "grey99", color = "black", size = 0.5)) #makes a box around the legend and adds a fill! 


  temperautre_plots[[df_name]] <- temp
}

temperautre_plots[[game]]
```


#GPU and CPU utilization
```{r}
utilization_plots <- list()

for (df_name in names(dfs_subset)) {
utilization <- ggplot(dfs_subset[[df_name]], aes(seconds)) +
  
    geom_line(aes(y = `CPUUtil(%)`, color = "CPU")) +
    
    geom_line(aes(y = `GPU1Util(%)`, color = "GPU")) +
  
  #Adding the average measure into the graph 
    annotate("text", x = -Inf, y = Inf,
         label = paste0("Avg CPU Util: ", round(mean(dfs_subset[[df_name]]$`CPUUtil(%)`), 2), "%", "\n",
                        "Avg GPU Util: ", round(mean(dfs_subset[[df_name]]$`GPU1Util(%)`), 2), "%"), 
         size = 2.5, color = "black", hjust = -0.05, vjust = 1.1) +
    
    labs(
      y = "Percent Utilized",
      x = "Time - (Minute:Seconds)", 
      title = paste0("Comparing utilization of CPU and GPU Over Time in ", df_name)
    ) +
    
    scale_y_continuous(breaks = seq(0, 100, by = 20),
                       limits = c(0, 100)) +
    
    scale_x_continuous(
      breaks = seq(0, max(dfs_subset[[df_name]]$seconds), by = 10),
      
      #sprintf() is a function in R that allows you to format strings with placeholders for variables. It takes two arguments: the format string and the variables to substitute into the string. The format string is a character string that includes placeholders for the variables.
      
      labels = function(x) sprintf("%2d:%02d", floor(x/60), x %% 60)
    ) +
    
    scale_color_manual(name = "", values = c("CPU" = "red", "GPU" = "blue")) +
  
    theme_clean() +
    
    theme(
         panel.grid.minor.y = element_line(color = "gray", linetype = "dotted"),
         legend.position = c(0.85, 0.90),
         legend.direction = "horizontal",
         legend.text = element_text(size = 6),
         legend.background = element_rect(fill = "grey99", color = "black", size = 0.5)) #makes a box around the legend and adds a fill! 

  utilization_plots[[df_name]] <- utilization
}

utilization_plots[[game]]
```


#CPU clock speed 
```{r}
cpu_clk_plots <- list()

for (df_name in names(dfs_subset)) {
CPU_cl <- ggplot(dfs_subset[[df_name]],aes(seconds)) +
  
    geom_line(aes(y = `CPUClk(MHz)`), color = "red") +
    
    labs(
      y = "CPU Speed (MHz)", 
      x = "Time - (Minute:Seconds)", 
      title = paste0("CPU clock Speed During game Run in ", df_name)
    ) +
  
    #Adding the average measure into the graph 
    annotate("text", x = -Inf, y = Inf,
         label = paste0("Avg CPU clk: ", round(mean(dfs_subset[[df_name]]$`CPUClk(MHz)`), 2)),
         size = 2.5, color = "black", hjust = -0.05, vjust = 1.1) +
    
    scale_x_continuous(
      breaks = seq(0, max(dfs_subset[[df_name]]$seconds), by = 20),
      
      #sprintf() is a function in R that allows you to format strings with placeholders for variables. It takes two arguments: the format string and the variables to substitute into the string. The format string is a character string that includes placeholders for the variables.
      labels = function(x) sprintf("%02d:%02d", floor(x/60), x %% 60)
    ) +
    
    scale_y_continuous(
      breaks = seq(3500, 5500, by = 250),
      limits = c(3500, 5500),
      minor_breaks = seq(3500, 5500, by = 125)) +
    
    #scale_color_manual(name = "Measures",
                       #value = "Core.Clocks..avg...MHz." = "blue") +
    
    theme_clean() +
    
    theme(panel.grid.minor.y = element_line(color = "gray", linetype = "dotted"),
         legend.position = c(0.65, 0.40),
         legend.title = element_text(size = 10.5), 
         legend.text = element_text(size = 10),
         legend.background = element_rect(fill = "grey99", color = "black", size = 0.5))  #makes a box around the legend and adds a fill! 

  cpu_clk_plots[[df_name]] <- CPU_cl
}

cpu_clk_plots[[game]]
```


#GPU clock speed 
```{r}
gpu_cl_plots <- list()

for (df_name in names(dfs_subset)) {
GPU_cl <- ggplot(dfs_subset[[df_name]], aes(seconds)) +
  
    geom_line(aes(y = `GPU1Clk(MHz)`), color = "red") +
    
    labs(
      y = "GPU Clock Speed (MHz)", 
      x = "Time - (Minute:Seconds)", 
      title = paste0("GPU clock Speed During game Run in ", df_name)
    ) +
  
    #Adding the average measure into the graph 
    annotate("text", x = -Inf, y = Inf,
         label = paste0("Avg GPU clk: ", round(mean(dfs_subset[[df_name]]$`GPU1Clk(MHz)`), 2)),
         size = 2.5, color = "black", hjust = -0.05, vjust = 1.1) +
    
    scale_x_continuous(
      breaks = seq(0, max(dfs_subset[[df_name]]$seconds), by = 20),
      
      #sprintf() is a function in R that allows you to format strings with placeholders for variables. It takes two arguments: the format string and the variables to substitute into the string. The format string is a character string that includes placeholders for the variables.
      labels = function(x) sprintf("%02d:%02d", floor(x/60), x %% 60)
    ) +
    
    #scale_y_continuous(
      #breaks = seq(3500, 5500, by = 250),
      #limits = c(3500, 5500),
      #minor_breaks = seq(3500, 5500, by = 125)) +
    
    #scale_color_manual(name = "Measures",
                       #value = "Core.Clocks..avg...MHz." = "blue") +
    
    theme_clean() +
    
    theme(panel.grid.minor.y = element_line(color = "gray", linetype = "dotted"),
         legend.position = c(0.65, 0.40),
         legend.title = element_text(size = 10.5), 
         legend.text = element_text(size = 10),
         legend.background = element_rect(fill = "grey99", color = "black", size = 0.5))  #makes a box around the legend and adds a fill! 
  
  gpu_cl_plots[[df_name]] <- GPU_cl
}

gpu_cl_plots[[game]]

```


###### Final 4 graphs are measured using hwinfo because of power consumption and fan utilization 

#GPU and CPU power consumption 
```{r}
power_plots <- list()

for (df_name in names(df_list_hw)) {

power <- ggplot(df_list_hw[[df_name]], aes(seconds)) +
  
  geom_line(aes(y = CPU.Package.Power..W., color = "CPU")) +
  
  geom_line(aes(y = GPU.PPT..W., color = "GPU")) +
  
  #Adding the average measure into the graph 
  annotate("text", x = -Inf, y = Inf,
       label = paste0("Avg CPU Power: ", round(mean(df_list_hw[[df_name]]$CPU.Package.Power..W.), 1), " W", "\n",
                      "Avg GPU Power: ", round(mean(df_list_hw[[df_name]]$GPU.PPT..W.), 1), " W"),
       size = 2.5, color = "black", hjust = -0.05, vjust = 1.1) +
    
  labs(
      y = "Power Draw (Watts)",
      x = "Time - (Minute:Seconds)", 
      title = paste0("Power Consumption of CPU and GPU Over Time in ", df_name)
    ) +
    
    scale_y_continuous(breaks = seq(0, 300, by = 50),
                       minor_breaks = seq(0, 300, by = 25),
                       limits = c(0, 300)) +
    
    scale_x_continuous(
      breaks = seq(0, max(df_list_hw[[df_name]]$seconds), by = 20),
      
      #sprintf() is a function in R that allows you to format strings with placeholders for variables. It takes two arguments: the format string and the variables to substitute into the string. The format string is a character string that includes placeholders for the variables.
      
      labels = function(x) sprintf("%2d:%02d", floor(x/60), x %% 60)
    ) +
    
    scale_color_manual(name = NULL, values = c("CPU" = "red", "GPU" = "blue")) +
    theme_clean() +
    
    theme(
         panel.grid.minor.y = element_line(color = "gray", linetype = "dotted"),
         legend.position = c(0.85, 0.92),
         legend.direction = "horizontal",
         legend.text = element_text(size = 6),
         legend.background = element_rect(fill = "grey99", color = "black", size = 0.5)) #makes a box around the legend and adds a fill! 

  power_plots[[df_name]] <- power
  rm(power)
}

power_plots[[game]]
```


#Fan speed for CPU & GPU coolers plus case fans 
```{r}
fan_speed_list <- list()

for (df_name in names(df_list_hw)) {
fan_speed <- ggplot(df_list_hw[[df_name]], aes(seconds)) +
  
    geom_line(aes(y = CPU..RPM., color = "CPU Fan")) +
    
    geom_line(aes(y = GPU.Fan..RPM., color = "GPU Fan")) +

    geom_line(aes(y = System.2..RPM., color = "Case")) + 
  
    #Adding the average measure into the graph 
    annotate("text", x = -Inf, y = Inf,
         label = paste0("Avg CPU Fan: ", round(mean(df_list_hw[[df_name]]$CPU..RPM.), 1), "\n",
                        "Avg GPU Fan: ", round(mean(df_list_hw[[df_name]]$GPU.Fan..RPM.), 1),"\n",
                        "Avg Case Fan: ", round(mean(df_list_hw[[df_name]]$System.2..RPM.), 1),"\n"),
         size = 2.5, color = "black", hjust = -0.05, vjust = 1.1) +

    labs(
      y = "Fan speed (RPM)",
      x = "Time - (Minute:Seconds)", 
      title = paste0("Fan Speed Over Time in ", df_name)
    ) +
    
    #scale_y_continuous(breaks = seq(0, 100, by = 20),
                       #limits = c(0, 100)) +
    
    scale_x_continuous(
      breaks = seq(0, max(df_list_hw[[df_name]]$seconds), by = 20),
      
      #sprintf() is a function in R that allows you to format strings with placeholders for variables. It takes two arguments: the format string and the variables to substitute into the string. The format string is a character string that includes placeholders for the variables.
      
      labels = function(x) sprintf("%2d:%02d", floor(x/60), x %% 60),
      minor_breaks = seq(0, max(df_list_hw[[df_name]]$seconds), by = 10),
    ) +
    
    scale_color_manual(name = NULL, values = c("CPU Fan" = "red", "GPU Fan" = "blue", "Case" = "green")) +
    theme_clean() +
    
    theme(
         panel.grid.minor.y = element_line(color = "gray", linetype = "dotted"),
         
         legend.text = element_text(size = 6),
         legend.background = element_rect(fill = "grey99", color = "black", size = 0.5)) #makes a box around the legend and adds a fill! 

  fan_speed_list[[df_name]] <- fan_speed
}

fan_speed_list[[game]]
```


#Temperature and power consuption CPU
```{r}
temp_power_cpu_list <- list()

for (df_name in names(df_list_hw)) {
  
temp_power_cpu <- ggplot(df_list_hw[[df_name]], aes(seconds)) +
  
  geom_line(aes(y = CPU.Package.Power..W., color = "CPU Power")) +
  
  geom_line(aes(y = CPU..Tctl.Tdie....C., color = "CPU Temp")) +
  
  #Adding the average measure into the graph 
  annotate("text", x = -Inf, y = Inf,
       label = paste0("Avg CPU Power: ", round(mean(df_list_hw[[df_name]]$CPU.Package.Power..W.), 1), " W", "\n",
                      "Avg CPU Temp: ", round(mean(df_list_hw[[df_name]]$CPU..Tctl.Tdie....C.), 1), " *C", "\n"),
       size = 2.5, color = "black", hjust = -0.05, vjust = 1.1) +
  
  labs(
    x = "Time (M:SS)", 
    title = paste0("CPU Power and Temperature Over Time in ", df_name)
  ) +
  
  scale_x_continuous(
    breaks = seq(0, max(df_list_hw[[df_name]]$seconds), by = 20),
    
    #sprintf() is a function in R that allows you to format strings with placeholders for variables. It takes two arguments: the format string and the variables to substitute into the string. The format string is a character string that includes placeholders for the variables.
    
    labels = function(x) sprintf("%02d:%02d", floor(x/60), x %% 60)
  ) +
  
  scale_y_continuous(name = "Power Draw (Watts)" ,
    sec.axis = sec_axis(~., name =  "Temperature (*C)")) +
    #breaks = seq(40, 80, by = 5),
    #minor_breaks = seq(40, 80, by = 2.5),
    #limits = c(40, 80)) +
  
  scale_color_manual(name = NULL,
                     values = c("CPU Power" = "red", "CPU Temp" = "blue")) +
  
  theme_clean() +
  
  theme(panel.grid.minor.y = element_line(color = "gray", linetype = "dotted"),
       legend.position = c(0.85, 0.90),
       legend.direction = "horizontal", 
       legend.text = element_text(size = 6),
       legend.background = element_rect(fill = "grey99", color = "black", size = 0.5)) + #makes a box around the legend and adds a fill! 
  
  guides(fill = guide_legend(reverse = TRUE)) 

  temp_power_cpu_list[[df_name]] <- temp_power_cpu
  
  rm(temp_power_cpu)
}

temp_power_cpu_list[[game]]


#The "cairo = FALSE" parameter should get rid of the anti aliasing on the cinebench text
#ggsave(filename = "my_plot.png", dpi = 300, cairo = FALSE)
```


#Temperature and power consuption GPU
```{r}
temp_power_gpu_list <- list()

for (df_name in names(df_list_hw)) {
  
temp_power_gpu <- ggplot(df_list_hw[[df_name]], aes(seconds)) +
  
  geom_line(aes(y = GPU.PPT..W., color = "GPU Power")) +
  
  geom_line(aes(y = GPU.Temperature...C., color = "GPU Temp")) +
  
  #Adding the average measure into the graph 
  annotate("text", x = -Inf, y = Inf,
       label = paste0("Avg GPU Power: ", round(mean(df_list_hw[[df_name]]$GPU.PPT..W.), 1), " W", "\n",
                      "Avg GPU Temp: ", round(mean(df_list_hw[[df_name]]$GPU.Temperature...C.), 1), " *C","\n"),
       size = 2.5, color = "black", hjust = -0.05, vjust = 1.1) +
  
  labs(
    x = "Time (M:SS)", 
    title = paste0("GPU Power and Temperature Over Time in ", df_name)
  ) +
  
  scale_x_continuous(
    breaks = seq(0, max(df_list_hw[[df_name]]$seconds), by = 20),
    
    #sprintf() is a function in R that allows you to format strings with placeholders for variables. It takes two arguments: the format string and the variables to substitute into the string. The format string is a character string that includes placeholders for the variables.
    
    labels = function(x) sprintf("%02d:%02d", floor(x/60), x %% 60)
  ) +
  
  scale_y_continuous(name = "Power Draw (Watts)" ,
    sec.axis = sec_axis(~., name =  "Temperature (*C)")) +
    #breaks = seq(40, 80, by = 5),
    #minor_breaks = seq(40, 80, by = 2.5),
    #limits = c(40, 80)) +
  
  scale_color_manual(name = NULL,
                     values = c("GPU Power" = "blue", "GPU Temp" = "red")) +
  
  theme_clean() +
  
  theme(panel.grid.minor.y = element_line(color = "gray", linetype = "dotted"),
       legend.direction = "horizontal",
       legend.position = c(0.85, 0.90),
       legend.text = element_text(size = 6),
       legend.background = element_rect(fill = "grey99", color = "black", size = 0.5)) + #makes a box around the legend and adds a fill! 
  
  guides(fill = guide_legend(reverse = TRUE)) 

  temp_power_gpu_list[[df_name]] <- temp_power_gpu
  
  rm(temp_power_gpu)
}

temp_power_gpu_list[[game]]
```



# Iterating over each list of graphs above and save them individually as a png for a report 
```{r eval=FALSE, include=FALSE}
#Create a list of lists with all the graphs we created above to loop through them and save each indivudal graph to its appropriate game file
List_of_list <- list(fan_speed_list, power_plots, gpu_cl_plots, cpu_clk_plots, utilization_plots, temperautre_plots, frametime_plots, temp_power_cpu_list, temp_power_gpu_list)

#Just adding names to the above lists to make looping through them easier 
names(List_of_list) <- c("fan_speed_list", "power_plots", "gpu_cl_plots", "cpu_clk_plots", "utilization_plots", "temperautre_plots", "frametime_plots", "temp_power_cpu_list", "temp_power_gpu_list")

# Defining the path we want to initially save all of the graphs before we sort by game 
path_name <- "C:/Users/Ryan/Coding Projects/Computer Benchmark/unsorted game graphs"

# Looping through each list saved in List_of_list then getting the number of graphs saved in that specific list (format of numbers is 1,2,3,4, 1,2,3,4,5,1,2,3,4,5,ect through each list of graphs)
#Then we extract the game name from each individual list to name the file later 
#Then we create the file name based on the list name from List_of_list and it's specific game graph we're saving 
for (name_list in seq_along(List_of_list)) {
  for (i in seq_along(List_of_list[[name_list]])) {
    
    game_name <- names(List_of_list[[name_list]][i])
                                       
    file_name <- paste0(names(List_of_list)[name_list], " - ", game_name, ".png")
    
    ggsave(List_of_list[[name_list]][[i]], file = file.path(path_name, file_name))
  }
}
```



#Averge FPS, 1%, and .1% lows for game tests 
```{r}
#Data Wrangling 

summary_fps <- read_excel(excel_file_frameview, sheet = "Summary")

#contains columns I might find important later but don't rn like `Min FPS`, `Max FPS`
summary_fps_o <- summary_fps %>% select(Application, `Avg FPS`, `1% Low FPS`, `0.1% Low FPS`, `Min FPS`, `Max FPS`)

summary_fps <- summary_fps %>% select(Application, `Avg FPS`, `1% Low FPS`, `0.1% Low FPS`)

#code to strip the .exe from the application variable so that it just displays the game name 
pattern <- "\\.exe$"

summary_fps$Application <- str_replace(summary_fps$Application, pattern, "")

#Code to calculate averages of "Avg FPS", "1% Low FPS", and "0.1% Low FPS" across game observations (the goal is 3 observations per game then take the averages of that)
summary_fps <- summary_fps %>% group_by(Application) %>%
  summarise('AVG FPS' = mean(`Avg FPS`),
            '1% Lows' = mean(`1% Low FPS`),
            '0.1% Lows' = mean(`0.1% Low FPS`))

#Pivoting the data to a longer format so that each of my FPS measures has their own column 
summary_fps_long <- pivot_longer(summary_fps, cols = c("AVG FPS", "1% Lows", "0.1% Lows"), names_to = "fps_type", values_to = "fps")

#Changing the names of the games in the application column to better fit 
summary_fps_long <- summary_fps_long %>% 
  mutate(Application = recode(Application, 
                              "FortniteClient-Win64-Shipping" = "Fortnite",
                              "starwarsbattlefrontii" = "SW Battlefront II",
                              "r5apex" = "Apex",
                              "cod" = "COD: Warzone",
                              "destiny2" = "Destiny 2"))

#Original
#hehe <- pivot_longer(summary_fps, cols = c("Avg FPS", "1% Low FPS", "0.1% Low FPS"), names_to = "fps_type", values_to = "fps")

#changing the format of the newly created FPS column so that it only displays out to 1 decimal point string to display all numbers 
summary_fps_long$fps <- round(summary_fps_long$fps, digits = 1)
```


```{r}
# Plot horizontal bar chart for all selected games 

fps_bar <- summary_fps_long %>% ggplot(aes(x =  fps, y = Application, fill = fps_type)) +
  geom_text(aes(label = fps), hjust = -0.1, position = position_dodge(width = 1)) +
  geom_bar(stat = "identity", position = "dodge") +
  
  labs(
    x = "FPS", 
    y = "Game", 
    fill = "",
    title = "Gaming Benchmarks July 2023",
    subtitle = "See spec sheet for specific computer configuration") +
  
  scale_fill_manual(values = c("AVG FPS" = "dodgerblue2", "1% Lows" = "firebrick3", "0.1% Lows" = "darkorange1")) +
  
#original
  #scale_fill_manual(values = c("Avg FPS" = "darkblue", "1% Low FPS" = "maroon", "0.1% Low FPS" = "yellow")) +
  
  scale_x_continuous(breaks = seq(0, 500, by = 100),
    limits = c(0, 500)) +
  #Reversing the legend does work in this case, but like in the KDL study I got around this by manually defining the factor levels for each variable 
  guides(fill = guide_legend(reverse = TRUE)) +
  theme_bw()

fps_bar
```



```{r eval=FALSE, include=FALSE}
#save the FPS bar chart to a PNG file on the desktop
ggsave(fps_bar, file = "C:/Users/Ryan/Coding Projects/Computer Benchmark/Game Graphs/All_FPS_barchart.png")
```